% =============================================
% BYLAWS CONTENT FILE
% Edit ONLY this file for content changes.
% Use normal LaTeX enumerate environments for all numbered/lettered lists.
% The formatting is handled automatically in main.tex
% =============================================

\JBArticle{rb-article-1}{ARTICLE I - SELECTION OF MEMBERS}
\begin{enumerate}
    \item The Appeals Board shall consist of five regular members and five alternate members. The regular members shall include two faculty, two students, and one staff representative. The alternate members shall be similarly apportioned.
    \item The Chair of the Faculty Senate shall annually appoint the regular and alternate faculty members. These appointments shall be made by November 5, and effective on January 1. Alternate members shall become regular members by replacement in their second year, effective January 1.
    \item The Grand Marshal shall annually appoint the regular and alternate student members for one-year terms, upon recommendation of the Appeals Board Chair (if already appointed) and Senior Judicial Administrator. These appointments shall be made by November 5, and effective on January 1.
    \item The President shall annually appoint the regular and alternative staff members. This appointment shall be made by November 5, and effective January 1. The alternate member shall become a regular member by replacement in his/her second year, effective on January 1.
    \item If a regular member should resign or be removed, an alternate member from the same constituency shall assume regular status. If an alternate membership should become vacant through resignation or early promotion, a new alternate member shall be appointed within 30 days.
    \item Appeals Board members shall meet to determine a Vice Chair from their ranks within 30 days following November 5.
\end{enumerate}

\JBArticle{rb-article-2}{ARTICLE II - RESPONSIBILITIES OF MEMBERS}
\begin{enumerate}
    \item The Appeals Board Chair shall have responsibility for facilitating the evidence Appeals process and shall preside over board meetings and hearings. The Chair will also coordinate/assist with all training in conjunction with the Senior Judicial Administrator in the Dean of Students Office.
    \item The Vice Chair shall assume the duties of the Chair in his or her absence.
    \item Members shall attend all meetings and hearings unless emergency extenuating circumstances exist. The Chair may recommend that a member be removed from the Board on the basis of unreasonable absence.
\end{enumerate}

\JBArticle{rb-article-3}{ARTICLE III - JURISDICTION}
\begin{enumerate}
    \item The Appeals Board is an appellate body that shall only consider appeals of the written decision of the lower body.
    \item Lower body is defined as the Student Judicial Board, the Greek Judicial Board, or the Faculty Academic Board.
\end{enumerate}

\JBArticle{rb-article-4}{ARTICLE IV - PROCEDURES}
\begin{enumerate}
    \item To initiate an appeal, an appellant must submit a written statement containing a specific reason for the appeal to the Chair of the Appeals Board in care of the Institute Judicial Administrator in the Dean of Students Office.
    \item At a closed meeting, based upon the written case materials, the Appeals Board shall determine one of four options:
    \begin{enumerate}
        \item uphold the decision of the lower body;
        \item modify the verdict or sanction of the lower body;
        \item refer the case back to the lower body with instructions for further action;
        \item conduct a hearing on the case.
    \end{enumerate}
    \item The Appeals Board can choose to deny the appeal, Appeals the entire case, or Appeals only part of the lower board's decision, (i.e., only the verdict, only the sanction, only one sanction, etc.)
    \item Appeals Board hearings shall be conducted as outlined in the Institute Hearing Procedures.
    \item Quorum for all meetings and hearings shall be five members, of which three shall be regular members.
    \item The appellant shall bear the burden of proof in all Appeals Board cases.
\end{enumerate}

\JBArticle{rb-article-5}{ARTICLE V - AMENDMENTS}
\begin{enumerate}
    \item Amendments to these by-laws must be consistent with Institute policy and protocol and shall require majority approval of the Appeals Board, followed by approval of the Institute President, the Faculty Senate and the Student Senate.
\end{enumerate}