% =============================================
% BYLAWS CONTENT FILE
% Edit ONLY this file for content changes.
% Use normal LaTeX enumerate environments for all numbered/lettered lists.
% The formatting is handled automatically in main.tex
% =============================================

\JBArticle{jb-article-1}{Article I: Organization}

\begin{enumerate}
\item The name of this organization shall be the Rensselaer Union Judicial Board, hereinafter referred to as the Judicial Board.
\item The Judicial Board gains its authority from the Rensselaer Union Constitution, the Student Handbook of Rights \& Responsibilities, and the Board of Trustees.
\item The Judicial Board shall be the primary court of judgment for cases in which student rights, responsibilities, or conduct is in question as defined by the Rensselaer Union Constitution.
\end{enumerate}

\JBArticle{jb-article-2}{Article II: Membership}

\begin{enumerate}
\item A Regular Member shall be defined as any person who has voting rights in the Judicial Board, as defined by the Rensselaer Union Constitution.
\item Judicial Board membership shall consist of the Judicial Board Chairperson, and Regular Members as defined by the Rensselaer Union Constitution.
\item An Alternate Member shall be defined as an individual who has the capacity to serve in the stead of a Regular Member for a given case or meeting, and shall be selected through the same process as a Regular Member.
  \begin{enumerate}
  \item The Alternate Member pool shall consist of a maximum of five members.
  \end{enumerate}
\item The membership of the Judicial Board, and the membership of the Alternate Member pool, shall be a matter of public record.
\end{enumerate}

\JBArticle{jb-article-3}{Article III: Officers}

\begin{enumerate}
\item The Judicial Board Chairperson is the presiding officer of the Judicial Board, hereinafter referred to as the Chairperson. Powers and duties of the Chairperson shall include:
  \begin{enumerate}
  \item The Chairperson shall be responsible for the functioning of the Judicial Board, and shall preside over all meetings and hearings.
  \item The Chairperson shall have the power to assign appropriate work to members.
  \item The Chairperson will have the responsibility of submitting a report of the activities of the Judicial Board, along with recommendations, to the Student Senate at the conclusion of the Fall and Spring academic semesters. This report will include statistics related to cases handled by the Judicial Board. The chairperson shall be the sole individual to determine any additional contents of this report.
  \item The Chairperson shall have the power to recommend removal, for good cause, of any member or Alternate to the Student Senate. It shall require a ⅔ vote of the Senate to remove the member.
  \end{enumerate}
\item The Chairperson shall nominate a Vice Chairperson from the voting membership of the Judicial Board. The Vice Chairman shall be confirmed by a ⅔ vote of the Judicial Board.
\item The Vice Chairperson shall assume the duties of the Chairperson, if the Chairperson is unable to fulfill those duties, or at the request of the Chairperson.
\item If the office of Judicial Board Chairperson becomes vacant, the Judicial Board shall fill the position as defined in the Union Constitution, within two weeks of the vacancy.
\end{enumerate}

\JBArticle{jb-article-4}{Article IV: Selection}

\begin{enumerate}
\item Members of the Judicial Board shall be appointed by the process outlined below.
  \begin{enumerate}
  \item The Judicial Board chairperson will solicit applications from the general Union membership.
  \item The membership of the selection committee shall consist of the following: The Judicial Board Chairperson, all active members of the Judicial Board, two representatives of the Student Senate, and a single representative of the Executive Board.
    \begin{enumerate}
    \item The Grand Marshal shall appoint the representatives of the Student Senate and the President of the Union shall appoint the representatives of the Executive Board.
    \item The Student Senate representatives shall share a single vote. The Executive Board representative shall have a single vote.
    \item All active members of the Judicial Board shall have one vote per.
    \end{enumerate}
  \item The Selection Committee shall at a minimum, interview all candidates appointed by the Judicial Board chairperson, and make a recommendation to the Student Senate to approve or deny the appointment.
    \begin{enumerate}
    \item At the discretion of the Chairperson, the Selection Committee may choose to interview all candidates, and advise the chairperson on their selection prior to the chairperson's appointments.
    \item The Judicial board chairperson may appoint members, regardless of the recommendation of the Selection Committee.
    \end{enumerate}
  \item The Judicial Board chairperson, in collaboration with the selection committee, will appoint Judicial Board members to be confirmed by the Student Senate.
  \end{enumerate}
\end{enumerate}

\JBArticle{jb-article-5}{Article V: Jurisdiction}

\begin{enumerate}
\item The Judicial Board shall have jurisdiction over all Union bodies or organizations as defined in the Union Constitution
\end{enumerate}

\JBArticle{jb-article-6}{Article VI: Business}

\begin{enumerate}
\item The Judicial Board shall have two types of meetings.
  \begin{enumerate}
  \item Hearings shall be those meetings held to consider cases. Quorum for hearings shall be four, and at least three of those present must be Regular Members. A ⅔ vote of those members present shall be required to approve any decision.
  \item Business meetings shall be those meetings called for any reason other than the hearing of a case. Quorum for business meetings shall be four Regular Members. It shall require a ⅔ vote of those Regular Members present to approve any action.
    \begin{enumerate}
    \item At least one business meeting will be held a semester.
    \end{enumerate}
  \end{enumerate}
\item At all business meetings of the Judicial Board, the chairperson shall extend an invitation to the Student Senate and the Executive Board, who may send no more than 2 individuals respectively. These individuals shall not be considered members of the Judicial Board. The chairperson may elect to share nonpublic information to these representatives.
\item If in any case the Judicial Board cannot reach quorum to hear a case in the required period of time, or in which the Board as a whole has a conflict of interest, the Chair may refer the case to the Review Board without a hearing by the Judicial Board.
\item A concise statement of each case, omitting names and other non-essential information, may be submitted to campus media at the conclusion of each case except when, at the discretion of the Chair and the Dean of Students, or appropriate designee, the statement would compromise confidentiality.
\end{enumerate}

\JBArticle{jb-article-7}{Article VII: Subordinate Judicial Bodies}

\begin{enumerate}
\item If the Judicial Board shall find that an excessive number of cases of a routine or minor nature are arising within any area, it may establish a subordinate judicial body.
\item The Judicial Board shall determine the jurisdiction, powers, and membership of subordinate judicial bodies.
\item All subordinate judicial bodies shall be chaired by a Judicial Board member or Alternate, appointed by the Judicial Board Chair and approved by ⅔ of the Senate.
\item Subordinate judicial bodies shall use the same procedures as Judicial Board, unless the Judicial Board explicitly provides otherwise.
\item Any decision made by a subordinate judicial body may be appealed to the Judicial Board as a whole provided the Grounds for Appeal are met.
\item The Student Motor Vehicle Court shall exist as a subordinate judicial body. Its Chair shall be a voting member of the Judicial Board. The Student Motor Vehicle Court Will be responsible for handling appeals for on campus parking tickets.
\end{enumerate}

\JBArticle{jb-article-8}{Article VIII: Amendments}

\begin{enumerate}
\item Amendments to these ByLaws shall require a ⅔ approval of the Judicial Board followed by a majority approval of the Student Senate.
  \begin{enumerate}
  \item After any revision to this document, it shall be distributed to all members of Union bodies, and made public to the Union membership.
  \end{enumerate}
\end{enumerate}
