% =============================================
% BYLAWS CONTENT FILE
% Edit ONLY this file for content changes.
% Use normal LaTeX enumerate environments for all numbered/lettered lists.
% The formatting is handled automatically in main.tex
% =============================================

\JBArticle{jb-article-1}{Article I: Organization}

\begin{enumerate}
\item 	The name of this organization shall be the Rensselaer Union Judicial Board or the RPI Judicial Board, hereinafter referred to as the Judicial Board. 
\item The Judicial Board gains its authority from the Rensselaer Union Constitution, the Student Handbook of Rights \& Responsibilities, and the Board of Trustees. 
\item  The Judicial Board is the primary court for cases involving student rights, responsibilities, or conduct, as defined by the Rensselaer Union Constitution. It has jurisdiction over all Union members, Union Bodies, and Union Organizations.
\begin{enumerate}
    \item Decisions of the Judicial Board may be appealed to the Review Board so long as grounds for appeal are met, unless noted otherwise in the bylaws.
    \item The appellant may request that the chairperson refer the case to the Review Board chairperson or may contact the Review Board chairperson directly.
\end{enumerate}
\end{enumerate}

\JBArticle{jb-article-2}{Article II: Membership}

\begin{enumerate}
\item A Member is an individual granted voting rights in all Judicial Board votes, as defined by the Rensselaer Union Constitution. 
\item An Alternate is an individual eligible to serve in the place of a Member, selected and confirmed using the same process as a Member.
\begin{enumerate}
    \item An Alternate may vote on behalf of a Member only when the Member recuses, loses voting eligibility, or otherwise cannot participate, and may only vote with the Member’s consent unless overruled by the remaining Members. 
    \item There is no limitation on the number of Alternates except as provided for in the Rensselaer Union Constitution. 
\end{enumerate}
\item Judicial Board membership includes the Chairperson, Members, and Alternates, as defined by the Rensselaer Union Constitution.
\item The membership of the Judicial Board, including Alternates, shall be a matter of public record. 
\end{enumerate}

\JBArticle{jb-article-3}{Article III: Officers}

\begin{enumerate}
\item The Chairperson is the presiding officer of the Judicial Board. The powers and duties of the Chairperson include: 
\begin{enumerate}
    \item The Chairperson shall be responsible for the Judicial Board's functioning and shall preside over all meetings and hearings
    \item The Chairperson shall have the power to assign appropriate work to members. 
    \item At the end of the Fall and Spring semesters, the Chairperson shall submit a public report of Judicial Board activities and case statistics to the Student Senate. The report may include any other content at the Chairperson's discretion.
    \item The Chairperson shall have the power to recommend removal, for good cause, of any Member or Alternate to the Student Senate. It shall require a ⅔ vote of the Senate to remove them. 
    \item The Chairperson shall have the power to appoint and demote officers, apart from the Vice Chair. 
    \item The Chairperson is responsible for all actions taken by the Board's officers.
    \item The Chairperson reserves the right to overrule, amend, or rescind any action taken by an officer.

\end{enumerate}
\item The Vice Chairperson shall assume the duties of the Chairperson if the Chairperson is unable to fulfill those duties, or at the Chairperson's request. 
\begin{enumerate}
    \item If the office of Vice Chairperson becomes vacant, any Member may declare candidacy to fill the role. The Judicial Board will conduct a vote among all remaining Members, and the candidate who receives the most votes will immediately assume the office of Vice Chairperson.
\end{enumerate}
\item If the Chairperson vacates the office, the Vice Chairperson shall immediately assume the role of Acting Chairperson. The Acting Chairperson will serve until a new Chairperson is selected in accordance with the process outlined in the Union Constitution.
\item The Chairperson may appoint the following officers from the Members and Alternates of the Judicial Board; these appointments are effective immediately. The duties of unfilled officer roles remain with the Chairperson.
\begin{enumerate}
    \item Recruitment Coordinator: The Recruitment Coordinator is responsible for recruiting new members, including postering on campus, coordinating publicity with other bodies, managing media relations, and overseeing public relations for the Board.
    \item Secretary: The Secretary is tasked with keeping meeting notes, preparing agendas, maintaining records and updates in the public record, and transcribing hearings.
    \item Historian: The Historian is charged with researching and informing the Board on relevant prior cases, assisting the Board in upholding precedent, maintaining knowledge of the Union Constitution and policies, and, in an unbiased manner, informing the Board of the applicable facts.
    \item Director of Civil Operations: The Director of Civil Operations coordinates all non-conduct cases, oversees arbitration, and oversees the training and assignment of SJAs for non-conduct cases.
    \item Treasurer: The Treasurer manages Board finances and budgeting and is responsible for ordering and tracking purchased items for Board use, such as food for hearings, uniforms, and other related expenses.
    \item Any Member of the Judicial Board may call for the demotion of an officer at any business meeting. Upon confirmation by a ⅔ majority of Members, the officer is demoted, and the Chairperson may not reappoint the same Member to the same role.
\end{enumerate}
\item Any Member or Officer exercising their role on the Judicial Board must keep the Board apprised of their actions. 
\item The Chairperson may, as needed, assign a representative of the Judicial Board from the membership to any person or organization. These representatives serve at the Chairperson's discretion. 
\item Any Member of the Judicial Board may propose a resolution of no confidence in the Chairperson or Vice Chairperson at any business meeting.
        \begin{enumerate}
            \item A resolution of no confidence shall require a ⅔ majority vote of Members to pass.
                \item If the resolution passes, the Chairperson or Vice Chairperson is relieved of their powers, and their duties are assumed by the other.
                \item In the case of the chairperson: a passed resolution of no confidence must be subsequently heard by the Senate. The Senate may take any of the following actions: 
            \begin{enumerate}
                \item Remove the subject of the resolution from the Judicial Board by a ⅔ vote.
            \end{enumerate}
            \begin{enumerate}
                \item Failure of the resolution to pass the Senate renders it void, and the subject may resume their duties.
            \end{enumerate}
        \item In the case of the vice chairperson: a passed resolution of no confidence removes the subject from office and the office is considered vacant.
    \end{enumerate}




\end{enumerate}



\JBArticle{jb-article-4}{Article IV: Selection}

\begin{enumerate}
    \item Membership of the Judicial Board shall be appointed in accordance with the process outlined below.
    \item The Judicial Board chairperson will solicit applications from the general Union membership.
    \item The selection committee consists of the Judicial Board Chairperson, all active Judicial Board members, two Student Senate representatives, and one Executive Board representative.
    \begin{enumerate}
        \item The Grand Marshal shall appoint the representatives of the Student Senate, and the President of the Union shall appoint the representative of the Executive Board.
        \item The Student Senate representatives shall share a single vote. The Executive Board representative shall have a single vote.
        \item All current Members of the Judicial Board shall have one vote each.
    \end{enumerate}
    \item The Selection Committee shall make a recommendation to the Student Senate to approve or deny the appointment.
    \begin{enumerate}
        \item At the Chairperson's discretion, the Selection Committee may interview all candidates and advise the Chairperson on their selection before the Chairperson's appointments.
        \item The Judicial Board chairperson retains final authority to appoint members to the Judicial Board, irrespective of the Selection Committee's recommendation.
    \end{enumerate}
    \item The Judicial Board chairperson, in collaboration with the selection committee, will appoint Judicial Board members, who will be confirmed by the Student Senate as outlined in the Union Constitution.
\end{enumerate}

\JBArticle{jb-article-5}{Article V: Communications}

\begin{enumerate}
    \item Official Communication is correspondence sent from jboard@rpi.edu to any party approved by a simple majority of Members.
    \item Unofficial Communication is any correspondence that is not an Official Communication.
    \begin{enumerate}
        \item Unofficial communications may be sent from jboard@rpi.edu if they specify they are not official and are signed by an active Member.
    \end{enumerate}
    \item Members and the Chairperson shall have access to jboard@rpi.edu; Alternates shall not have such access.
    \item Official Communications become part of the public record upon conclusion of the related matter, unless publication would violate policies regarding anonymity, confidentiality, or other Institute rules.
    \begin{enumerate}
        \item Communications, or portions thereof, that must remain confidential due to anonymity, policy, or other restrictions shall be withheld or censored at the discretion of the Chairperson.
        \begin{enumerate}
            \item The decision of the Chairperson may be overruled by a simple majority of Members.
            \item The release of Communications may be revisited by the Chairperson or the board at any time after a decision.
        \end{enumerate}
        \item When content is withheld, a general statement will replace or append the communication in the public record, stating what was withheld and the rationale for doing so.
    \end{enumerate}
    \item Judicial Board Members may not share confidential or case-related information with any external party without the express consent of the Chairperson.
    \begin{enumerate}
        \item The decision of the Chairperson may be overruled by a ⅔ majority of Members.
    \end{enumerate}
\end{enumerate}

\JBArticle{jb-article-6}{Article VI: Meetings}
\begin{enumerate}
  \item The Judicial Board shall have three types of meetings.
  \begin{enumerate}
    \item Business meetings refer to all meetings regarding Board operations. Quorum for business meetings shall be four Members. It shall require a ⅔ vote of those Members present to approve any action unless otherwise specified.
      \begin{enumerate}
        \item At least one business meeting will be held in a semester.
        \item Business meetings are open to members of the Student Government unless otherwise specified by the Judicial Board Chairperson.
      \end{enumerate}
    \item Hearings refer to all meetings that issue a verdict on a case. Quorum for hearings shall be four, and at least three of those present must be Members. A ⅔ vote of those members present shall be required to approve any decision. Judicial Board hearing procedures are defined by the Institute Hearing Procedures \textit{(as updated on November 15, 1996).}
      \begin{enumerate}
        \item The Institute Hearing Procedures may be released upon request by the Dean of Students' Office.
      \end{enumerate}
    \item Inquiries refer to all meetings that discuss case matters that do not issue a verdict. Quorum for inquiries shall be four, and at least three of those present must be Members. A ⅔ vote of those members present shall be required to approve any decision.
      \begin{enumerate}
        \item Conduct Cases may not be discussed in Inquiries.
      \end{enumerate}
  \end{enumerate}
  \item The Judicial Board can refer any case directly to the Review Board by majority vote.
  \item A concise statement of each case, omitting names and other non-essential information, may be submitted to campus media at the conclusion of each case except when, at the discretion of the Chair and the Dean of Students, or appropriate designee, the statement would compromise confidentiality.
\end{enumerate}


\JBArticle{jb-article-7}{Article VII: Case Procedure}
\begin{enumerate}
  \item The Judicial Board defines 3 types of cases that it can hear. The Judicial Board reserves the right to manage the logistics of cases at its discretion to adhere to these bylaws.
    \begin{enumerate}
      \item Conduct Cases refer to all cases referred to the Judicial Board by the Office of the Dean of Students.
        \begin{enumerate}
          \item The Judicial Board will refer violations of Grounds for Disciplinary Action and Institute Policy to the Office of the Dean of Students if submitted by a body other than the Office of the Dean of Students.
        \end{enumerate}
      \item Civil Cases refer to all matters alleging the violation of Union Policy by an individual or group.
      \item Constitutional Cases are based on petitions alleging the violation of the Union Constitution.
    \end{enumerate}
  \item Any member of the Union, member of the Institute community, Union body, or Union organization may request a Student Judicial Advisor (SJA) for any reason.
    \begin{enumerate}
      \item SJAs may be either a Member or an Alternate of the Judicial Board. Any party may request a specific Member or Alternate of the Judicial Board to serve as their SJA, except the Chairperson.
      \item In conduct cases, the SJA is assigned by the Chairperson.
      \item The role of the SJA in conduct cases is limited to the following:
        \begin{enumerate}
          \item Communication of the Institute Judicial Process to the assigned party, including answering all relevant questions.
          \item Attending hearings at the request of the assigned party. However, the SJA cannot speak during conduct hearings.
          \item The SJA does not provide legal counsel or advocate for the party they are assigned to. SJAs cannot aid in case preparation.
          \item The Office of the Dean of Students governs the conduct of the SJA in all cases referred to the Judicial Board through the Institute’s conduct process.
        \end{enumerate}
      \item SJAs are governed by the following policies in civil and constitutional matters:
        \begin{enumerate}
          \item The SJA will act as the counsel for the assigned party.
          \item No SJA may act against the interests of the party to whom they are assigned. Breach of this duty constitutes grounds for immediate removal as SJA.
          \item The SJA cannot share any information with the Judicial Board without the party’s explicit consent.
          \item The SJA shall not vote as a Member of the Judicial Board in any proceeding in which a party to whom they are appointed is a party named in the case, nor shall they be present during deliberation.
          \item The SJA may attend inquiries and hearings with the consent of the Judicial Board and shall step out at any time upon the request of the Chairperson.
        \end{enumerate}
    \end{enumerate}
  \item Any member of the Union, member of the Institute community, Union body, or Union organization may submit a petition to the Judicial Board. The party submitting the petition shall be known as the ``complainant''.
    \begin{enumerate}
      \item Any member of the Union, member of the Institute community, Union body, or Union organization may also request a Student Judicial Advisor before submitting a petition to aid with drafting a petition. The request for an SJA does not obligate the party to submit a petition.
      \item An initial petition to the Judicial Board shall contain the following information:
        \begin{enumerate}
          \item Any and all referenced policies and documentation of incidents related to the petition.
          \item A brief reasoning as to why the complainant believes the respondent is in violation.
          \item Specific relief sought.
        \end{enumerate}
      \item The Judicial Board reserves the right to evaluate and dismiss petitions unless they satisfy one of the following:
        \begin{enumerate}
          \item If the petition is submitted by a Union body, and the Union body votes by majority, it will proceed to an inquiry or hearing.
          \item Petitions related to incidents more than one semester old from the incident in question will generally not be heard.
          \item The Judicial Board reserves the right to divide a petition into multiple cases if assertions made in the petition fall into different case types.
          \item The Judicial Board will hold an inquiry meeting to determine the validity of a petition. If a petition is considered valid, it is henceforth considered a case. If the petition is invalid, official notice is sent to the complainant dismissing the case.
        \end{enumerate}
      \item A petition may request an injunction against an action.
        \begin{enumerate}
          \item If a petition requests an injunction, an inquiry meeting will be held within 24 hours to vote on granting the injunction.
        \end{enumerate}
    \end{enumerate}
  \item Once a case is established, the Judicial Board Chairperson shall notify all involved parties.
    \begin{enumerate}
      \item For the purpose of these procedures, the ``complainant'' shall be the party bringing the appeal. The ``respondent'' shall be the affected party (or parties) responsible for the actions in question.
      \item The respondent may choose to concede the case at this point, as defined in the types of case resolutions.
      \item If, after a reasonable time period has elapsed, and the complainant does not believe the matter has been settled by the respondent, they may reissue the petition. The respondent shall not be allowed to concede the case for a reissued petition.
      \item Both the complainant and the respondent shall be provided with a copy of the initial petition and a reasonable timeframe to prepare an initial argument for their side.
        \begin{enumerate}
          \item In providing copies of the initial petition to both sides, the Judicial Board Chairperson may redact personal information as is reasonable to protect anonymity.
          \item Failure to submit an argument shall not be considered as conceding the case. The Judicial Board Chairperson must make reasonable efforts and accommodations for either party to submit an argument.
        \end{enumerate}
    \end{enumerate}
  \item Each side will be provided with all arguments and given a reasonable timeframe to write a counterargument.
    \begin{enumerate}
      \item Either side may choose to concede its case at this point, in which the case would be concluded via Concession.
      \item Failure to submit a counterargument shall not be considered as conceding the case. The Judicial Board Chairperson shall make reasonable efforts and accommodations for either party to submit an argument.
      \item The initial petition, arguments, and counterarguments shall be compiled into an evidence packet.
    \end{enumerate}
  \item Once established, cases may conclude one of four ways.
    \begin{enumerate}
      \item Concession: After the establishment of a case, the respondent may immediately concede the case. In doing so, the Judicial Board shall take no further actions, and the respondent shall be responsible for resolving the issue.
        \begin{enumerate}
          \item Concessions must be written and submitted to the Judicial Board.
        \end{enumerate}
      \item Arbitration Agreement: As mediated by the Judicial Board, the parties may come to an agreement on the pertinent matters. A written statement, signed by all affected parties, outlining the specifics of an agreement addressing the totality of a case to the satisfaction of the Judicial Board, may conclude a case.
      \item Dismissal: After a judicious review of case materials and ensuring jurisprudential propriety, the Board may dismiss a case when warranted by evidence or procedural considerations. In such instances, the Board must provide a written rationale detailing the grounds for dismissal. Dismissal shall not be exercised in a manner that obstructs justice, restricts the rights of complainants, or silences their grievances.
        \begin{enumerate}
          \item Dismissals are appealable to the Review Board, which may direct the Judicial Board to hear the case, hear the case themselves, or exercise their appellate authority in any fashion deemed appropriate.
        \end{enumerate}
      \item Verdict: In concluding a hearing, a verdict is issued. Verdicts are binding, and the conclusions on the relevant matters are enforceable by sanctions.
        \begin{enumerate}
          \item After issuing a verdict, the Judicial Board shall write an assenting and a dissenting opinion, if they are not in unanimous agreement, explaining their decision on the case. Such opinions shall be considered public record and shall be delivered directly to all Union bodies and campus publications.
        \end{enumerate}
    \end{enumerate}
  \item Arbitration shall be available only in circumstances where all parties express written consent to participate in arbitration after a petition has become a case. Requests for arbitration are approved at an inquiry meeting of the Judicial Board and can be submitted at any time after the case is initiated, prior to a hearing. Arbitration is not permitted for conduct cases.
    \begin{enumerate}
      \item The Judicial Board may deny any arbitration request for any reason it determines appropriate, provided that the decision to deny is accompanied by a written explanation of the rationale.
      \item The Judicial Board shall not permit the imposition of penalties, sanctions, or disciplinary action that would require a hearing.
      \item The arbitrator shall be appointed from among the membership of the Judicial Board, as the Chairperson or designee may select. Such appointment shall be subject to the unanimous consent of the Judicial Board.
      \item The arbitrator shall ensure that all proceedings are conducted fairly, neutrally, and with due regard to confidentiality.
        \begin{enumerate}
          \item The arbitrator is responsible for ensuring the arbitration agreement complies with Union policy.
          \item The arbitrator cannot discuss the arbitration terms unless representatives for the respondent and the complainant are present.
        \end{enumerate}
      \item Any resolution reached through Judicial Board arbitration shall become binding only upon the written consent of all parties and the Judicial Board's acknowledgment. The Judicial Board reserves the right to reject or refuse to enforce any agreement that is inconsistent with Union policy or governing law.
      \item Arbitration agreements must be submitted in writing to the Judicial Board and are a matter of public record unless both parties agree to ``seal'' the agreement, in which case a copy is retained by the Judicial Board but not released publicly.
    \end{enumerate}
  \item A hearing is scheduled once the counterarguments have been submitted, in accordance with the Institute's Hearing Procedures.
\end{enumerate}

 \JBArticle{jb-article-8}{Article VIII: Conduct Procedures}

\begin{enumerate}
    \item The procedures for conduct cases are overseen in collaboration with the Dean of Students or an appropriate designee and are bound by the Institute Hearing Procedure as adopted by the Board of Trustees.
\end{enumerate}


\JBArticle{jb-article-9}{Article IX: Subordinate Judicial Bodies}

\begin{enumerate}
\item If the Judicial Board determines that an excessive number of routine or minor cases are arising in any area, it may establish a subordinate judicial body to address them. 
\item The Judicial Board shall define the jurisdiction, powers, and membership of each subordinate judicial body, and these shall be outlined in that body’s bylaws. 
\item Each subordinate judicial body shall be chaired by a Judicial Board member or Alternate, appointed by the Judicial Board Chair and approved by a two-thirds (2/3) vote of the Senate.
\item Unless expressly modified by the Judicial Board in the bylaws of a subordinate judicial body, the procedures of the Judicial Board shall apply to all subordinate judicial bodies. 
\item Any decision of a subordinate judicial body may be appealed to the Judicial Board as a whole, provided the established Grounds for Appeal are satisfied. 
\item The bylaws governing subordinate judicial bodies shall be part of the public record. 
\item The bylaws of subordinate judicial bodies are deemed bylaws of the Judicial Board and may not be amended by the subordinate bodies themselves. Any amendments to such bylaws shall follow the same procedure as amendments to the Judicial Board bylaws.
\end{enumerate}

\JBArticle{jb-article-10}{Article X: Amendments}

\begin{enumerate}
\item Amendments to these Bylaws shall require a ⅔ approval of the Judicial Board, followed by a majority approval of the Student Senate. 
  \begin{enumerate}
  \item Revisions of these bylaws shall be a matter of public record.
  \end{enumerate}
\end{enumerate}
